Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
Replace "species x" with "population x"

Different perceptions of the proportion of each stock in an area are seen when
we aggregate the data over a smaller geographical region at different
timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
the true population, the monthly aggregation captures the major patterns of
composition seen in the weekly data with the percentage of different species in
the catch having similar mean and standard deviations.  In the weekly data
species 1 = 9.36 (3.99), species 2 = 83.2 (5.60), species 3 = 3.57 (1.23),
species 4 = 3.91 (1.59); in the monthly data species 1 = 9.23 (3.87), species 2
= 83.3 (5.52), species 3 = 3.62 (1.15), species 4 = 3.86 (1.52). While means
were similar some of the variation was lost when aggregated to an annual level;
species 1 = 9.90 (0.173), species 2 = 82.2 (0.308), species 3 = 3.82 (0.119),
species 4 = 4.03 (0.0502).\\

The commercial data on a weekly basis shows some of the same patterns as the
true population, though the species 1 (in red) is less well represented and
some weeks are missing catches from the area. Here, weekly and monthly
compositions were nearly identical, with monthly composition of species 1 =
0.0472 (0.0139), species 2 = 94.4 (1.47), species 3 = 3.12 (1.47), species 4 =
2.40 (0.444). Again, yearly values head a similar mean but smaller standard
deviation.\\

The survey data was only available on an annual basis, and showed again a
slightly different composition; species 1 = 0.372 (0.00473), species 2 = 87.7
(0.193), species 3 = 0.729 (0.0200), species 4 = 11.2 (0.172).

@@

We implemented a spatial closure using the different data sources and spatial
and temporal aggregations as outlined in the protocol in Section 3.4. We used
this to assess the efficacy of a closure in reducing fishing mortality on
species 3, given availability of data and its use at different resolutions in
order to evaluate the trade-offs in data sources.

The trend in fishing mortality for each species show that in most cases the
fishery closure was successful in reducing fishing mortality on the species of
interest (species 3; Figure \ref{fig:3}), though interestingly the largest
reductions in fishing mortality happened immediately after the closures,
following which the fisheries ``adapted" to the closures and fishing mortality
increased again somewhat. The exception to the success was the closures
implemented based on the coarsest spatial (20 x 20) and temporal resolution
(yearly) that was ineffective with all data sources. As expected, closures
based on the ``known" population distribution were most effective, with
differing degrees of success using the commercial data. Fishing mortality rates
on the other species changed in different proportions, depending on whether the
displaced fishing effort moved to areas where the populations were found in
greater or lesser density. \\

@@

The yearly data assumes the same proportion of each population caught at any
time of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The monthly data shows some consistency between the real
population and commercial data for species 2 - 4, though species 1 remains
under-represented.  On an annual basis, interestingly the commercial data under
represents the first species (in red) while the survey over represents species
1. This is likely due to the biases in commercial sampling, with the fisheries
not targeting the areas where species 1 are present and the survey sampling
areas where species 1 is more abundant than on average. This indicates that
fixed closures, at the right resolution, when based on commercially derived
data have the potential to reduced fishing mortality. The likely cost of poor
spatial and temporal resolution is associated with reduced effectiveness and
potentially closing fishing opportunities for other fisheries. \\

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{Closure fishing locations based on annual closures with a
		coarse spatial resolution. Closure location can be seen in red
	in relation to a) before the closure fishing locations, b) after the
	closure fishing locations, c) species 3 habitat distribution.}
	\label{fig:17}
\end{figure}	
%\end{comment}

>>>>

Different perceptions of the proportion of each stock in an area are seen when
we aggregate the data over a smaller geographical region at different
timescales, with weekly (top), monthly (middle) and yearly (bottom) catch
compositions from across an aggregated 20 x 20 area (Figure \ref{fig:2}). In
the true population, the monthly aggregation captures the major patterns of
composition seen in the weekly data with the percentage of different species in
the catch having similar mean and standard deviations.  In the weekly data
population 1 = 9.36 (3.99), population 2 = 83.2 (5.60), population 3 = 3.57 (1.23),
population 4 = 3.91 (1.59); in the monthly data population 1 = 9.23 (3.87), population 2
= 83.3 (5.52), population 3 = 3.62 (1.15), population 4 = 3.86 (1.52). While means
were similar some of the variation was lost when aggregated to an annual level;
population 1 = 9.90 (0.173), population 2 = 82.2 (0.308), population 3 = 3.82 (0.119),
population 4 = 4.03 (0.0502).\\

The commercial data on a weekly basis shows some of the same patterns as the
true population, though the population 1 (in red) is less well represented and
some weeks are missing catches from the area. Here, weekly and monthly
compositions were nearly identical, with monthly composition of population 1 =
0.0472 (0.0139), population 2 = 94.4 (1.47), population 3 = 3.12 (1.47), population 4 =
2.40 (0.444). Again, yearly values head a similar mean but smaller standard
deviation.\\

The survey data was only available on an annual basis, and showed again a
slightly different composition; population 1 = 0.372 (0.00473), population 2 = 87.7
(0.193), population 3 = 0.729 (0.0200), population 4 = 11.2 (0.172).

@@

We implemented a spatial closure using the different data sources and spatial
and temporal aggregations as outlined in the protocol in Section 3.4. We used
this to assess the efficacy of a closure in reducing fishing mortality on
population 3, given availability of data and its use at different resolutions in
order to evaluate the trade-offs in data sources.

The trend in fishing mortality for each species show that in most cases the
fishery closure was successful in reducing fishing mortality on the species of
interest (population 3; Figure \ref{fig:3}), though interestingly the largest
reductions in fishing mortality happened immediately after the closures,
following which the fisheries ``adapted" to the closures and fishing mortality
increased again somewhat. The exception to the success was the closures
implemented based on the coarsest spatial (20 x 20) and temporal resolution
(yearly) that was ineffective with all data sources. As expected, closures
based on the ``known" population distribution were most effective, with
differing degrees of success using the commercial data. Fishing mortality rates
on the other species changed in different proportions, depending on whether the
displaced fishing effort moved to areas where the populations were found in
greater or lesser density. \\

@@

The yearly data assumes the same proportion of each population caught at any
time of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The monthly data shows some consistency between the real
population and commercial data for population 2 - 4, though population 1 remains
under-represented.  On an annual basis, interestingly the commercial data under
represents the first species (in red) while the survey over represents species
1. This is likely due to the biases in commercial sampling, with the fisheries
not targeting the areas where population 1 are present and the survey sampling
areas where population 1 is more abundant than on average. This indicates that
fixed closures, at the right resolution, when based on commercially derived
data have the potential to reduced fishing mortality. The likely cost of poor
spatial and temporal resolution is associated with reduced effectiveness and
potentially closing fishing opportunities for other fisheries. \\

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{Closure fishing locations based on annual closures with a
		coarse spatial resolution. Closure location can be seen in red
		box in relation to a) before the closure fishing locations, b)
		after the closure fishing locations, c) population 3 habitat
		distribution.}
	\label{fig:17}
\end{figure}	
%\end{comment}
